---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/"
)
set.seed(0)
```

# BoundedCoalescent

BoundedCoalescent is a R package to simulate and compute the probability of phylogenies
under the bounded coalescent model. This model is obtained by conditioning the standard
coalescent so that the most recent ancestor of the whole sample occurs after a set date.

## Installation

You can install BoundedCoalescent from github with:

```{r gh-installation, eval = FALSE}
devtools::install_github("DrJCarson/BoundedCoalescent")
```

The package can then be loaded using:
```{r}
library(BoundedCoalescent)
```


## More information and getting help

For more detailed examples of how to use BoundedCoalescent, see the vignettes [here](https://github.com/DrJCarson/BoundedCoalescent/tree/master/vignettes).
See also the help included in the package using the R command
`help(package='BoundedCoalescent')`. 

If you have any problem or question please create an issue [here](https://github.com/DrJCarson/BoundedCoalescent/issues). 
