---
title: "Demonstration of the BoundedCoalescent package"
date: '`r Sys.Date()`'
output:
  pdf_document: default
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Demonstration of the BoundedCoalescent package}
  %\usepackage[utf8]{inputenc}
---

In this vignette we demonstrate the use of the BoundedCoalescent package.

# Initialisation

```{r}
library(BoundedCoalescent)
library(ape)
set.seed(0)
```

# Simulation of a phylogeny


The BoundedCoalescent package can simulate dated phylogenies under the bounded coalescent model.
For example, here we simulate a tree with 5 leaves each in 2020, 2021 and 2022, with an effective population size $N_e=2$ and a bound in 2019:

```{r}
t=bounded_sample_phylo(c(2020,2021,2022),c(5,5,5),2,2019)
plot(t$phylo)
axisPhylo(1,backward = F)
```

# Probability of a phylogeny

The BoundedCoalescent package can calculate the probability of a dated phylogeny under the bounded coalescent model.
For example, here we generate a random tree with the ape package function rtree, set its root date to 2020:

```{r}
t=rtree(20)
t$root.time=2020
plot(t)
axisPhylo(1,backward = F)
```

We can calculate the probability of this tree under the bounded coalescent model with effective population size  $N_e=2$ and a bound in 2019:

```{r}
bounded_likelihood_phylo(t,2,2019)
```


# Bound probability

The BoundedCoalescent package can calculate the probability that unbounded coalescent tree will have its root after a certain date. For example, if we consider a tree with five leaves in 2020 and five leaves in 2021, under the unbounded coalescent model with effective population size $N_e=2$, the probability that the root occurs after 2019 is:

```{r}
bounded_forward_algorithm(c(2020,2021),c(5,5),2,2019)$bound_probability
```
